ManuscriptFigures

### 2024-02-23 Code/ManuscriptFigures.Rmd
Generated PUR estimate figures

# ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

# MIT9313OverlayPlots <- PURPARFits %>%
PURPARFits %>%
   filter(Strain == "MIT9313",
          O2_Category == "High",
          Par_ue == 30,
          Photoperiod == 12 & WL == 450 |
          Photoperiod == 12 & WL == 530 |
          Photoperiod == 12 & WL == 660 |
          Photoperiod == 16 & WL == "WW") %>% 
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

 # MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
 # 
 # MIT9313OverlayPlots
```

@@

# ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

```{r SS120 PUR overlay with legend,  fig.height = 10, fig.width = 10}
# SS120OverlayPlots <- PURPARFits %>%
PURPARFits %>%
   filter(Strain == "SS120",
          O2_Category == "High",
          Par_ue == 30,
          Photoperiod == 8 |
          Photoperiod == 12 & WL == 530,
          Run != 113 & Run != 112) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
 scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both))+
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

 # SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
 # 
 # SS120OverlayPlots

@@

# ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

MIT9313OverlayPlots <- PURPARFits %>%
   filter(Strain == "MIT9313",
          O2_Category == "High",
          Par_ue == 30,
          Photoperiod == 12 & WL == 450 |
          Photoperiod == 12 & WL == 530 |
          Photoperiod == 12 & WL == 660 |
          Photoperiod == 16 & WL == "WW") %>% 
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

 MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

 MIT9313OverlayPlots
```

@@

ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

```{r SS120 PUR overlay with legend,  fig.height = 10, fig.width = 10}

 SS120OverlayPlots <- PURPARFits %>%
   filter(Strain == "SS120",
          O2_Category == "High",
          Par_ue == 30,
          Photoperiod == 8 |
          Photoperiod == 12 & WL == 530,
          Run != 113 & Run != 112) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
 scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both))+
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

 SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

 SS120OverlayPlots

@@

ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
